Analysis PPM-S

### 2020-07-30 production/prod_analysis-cfa.rmd
likert, corplot, tablefit, sempath, bib, preanalisis

table01<- bind_cols(x = matpolyw01,y = load01)
# %>% mutate(vars=labs)

@@

table02<- bind_cols(x = matpolyw02,y = load02)
# %>% mutate(vars=labs)

@@

table03<- bind_cols(x = matpolyw03,y = load03)
# %>% mutate(vars=labs)

@@

table03tau<- bind_cols(x = matpolyw03tau,y = load03tau) 
# %>% mutate(vars=labs)

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A.Perception Effort", "B.Perception Talent","C.Perception Rich parents","D.Perception contacts","E.Preferences Effort","F.Preferences Talent","G.Preferences rich parents", "H.Preferences contacts" )
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
save(cor04, file = "output/images/correlation.RData")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)

@@

@@

@@

@@

plotlikert<-plot_likert(dat_merit, c(1,1,1,1,2,2,2,2),
            groups.titles = c("Perceptions","Preferences"),
            geom.colors ="PuBu", 
            geom.size = 0.8,
            axis.labels=c("Effort","Talent","Rich Parents","Contacts"),
            catcount = 4,
            cat.neutral = 3, 
            grid.range  =  c ( 1.2 , 1.4 ),
            values  =  "sum.outside",
            reverse.scale=TRUE)
plotlikert

ggsave(plotlikert,filename = "output/images/plotlikert.png",device = "png",width = 18,height = 15,dpi = "retina",units = "cm")

>>>>

table01<- bind_cols(x = matpolyw01,y = load01)
### %>% mutate(vars=labs)

@@

table02<- bind_cols(x = matpolyw02,y = load02)
## %>% mutate(vars=labs)

@@

table03<- bind_cols(x = matpolyw03,y = load03)
   ## %>% mutate(vars=labs)

@@

table03tau<- bind_cols(x = matpolyw03tau,y = load03tau) 
### %>% mutate(vars=labs)

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A.Perception Effort", "B.Perception Talent","C.Perception Rich parents","D.Perception contacts","E.Preferences Effort","F.Preferences Talent","G.Preferences rich parents", "H.Preferences contacts" )
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
save(cor04, file = "output/images/correlation.RData")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = TRUE)

@@

corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = TRUE)

@@

semPaths(fit4_o , 
whatLabels = "std",
what="col",
label.cex=1,
edge.label.cex=1,
residuals=F, 
edge.color = "black",
style = "lisrel",
fade=F, 
nCharNodes = 0,
 curvePivot = FALSE,
         curve = 2,
rotation = 4,
layout = "tree3",
         cardinal = "lat cov",  
legend.cex = 0.6,
         label.cex =1,
label.font = 6,
         edge.label.font= 1,
         asize = 3,
edge.width =1,
         sizeMan=5,
         sizeLat = 10, width = 12,
         height= 15, nodeNames = nodeNames, intercepts = F, reorder = F, thresholds = F, nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"), filetype ="png", filename = "output/images/meas01") #arrow size)

@@

```{r}
sum_fit<- bind_rows(fitmeasures(fit4_o)[c("chisq.scaled","df","cfi.scaled","rmsea","rmsea.scaled")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi.scaled","rmsea","rmsea.scaled")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi.scaled","rmsea","rmsea.scaled")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi.scaled","rmsea","rmsea.scaled")])
sum_fit$mod <- c("Model 1","Model 2","Model 3","Model 4")
sum_fit$est <- c("DWLS","DWLS","DWLS","DWLS")
sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI.sca","RMSEA","RMSEA.sca")

sumtable02<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Complete sample",
                          "Model 2: fixed order by percepction/preference",
                          "Model 3:  fixed order by topic (i.e: effort)",
                          "Model 4: Randomized order"));sumtable02
```

@@

dat_merit_2<- dat_merit %>% sjmisc::rec(rec="rev") %>% select("a.Effort"=a.Effort_r,"a.Talent"=a.Talent_r, "a.Rich Parents"="a.Rich Parents_r", "a.Contacts"=a.Contacts_r, "b.Effort"=b.Effort_r,"b.Talent"=b.Talent_r,"b.Rich Parents"="b.Rich Parents_r", "b.Contacts"=b.Contacts_r)

plotlikert<-plot_likert(dat_merit_2, c(1,1,1,1,2,2,2,2),
            groups.titles = c("Perceptions","Preferences"),
            geom.colors ="PuBu", 
            geom.size = 0.8,
            axis.labels=c("Effort","Talent","Rich Parents","Contacts"),
            catcount = 4,
            cat.neutral = 3, 
            grid.range  =  c ( 1.2 , 1.4 ),
            values  =  "sum.outside", reverse.colors = T)
plotlikert

ggsave(plotlikert,filename = "output/images/plotlikert.png",device = "png",width = 25,height = 15,dpi = "retina",units = "cm")
